---
title: 9.29.2017 Class Notes
author: Steven Koski
date: '2017-10-02'
slug: 9-29-2017-class-notes
categories:
  - R
tags:
  - R Markdown

---
```{r}
library(Lahman)
library(sqldf)
library(ggplot2)
```

```{r}
print("This next code is an example of a scatterplot we learned in class. It gathers all the data and plots thm as dots on a graph to make it easier to visualize the data. We also draw lines between each of the data points to make it easier to visualize how the points are ordered.")
#This is a scatterplot that has two columns of numerical data and one 
#represents time wile the other reperesents different points of data
query<-"SELECT yearID,HR
FROM Batting 
WHERE playerID='ruthba01'"

result<-sqldf(query)

ggplot()+
  geom_point(data=result,aes(x=yearID,y=HR))+
  geom_line(data=result,aes(x=yearID,y=HR))+
  ggtitle("Home Runs Per Year for Babe Ruth")+
  xlab("Year")+
  ylab("Home Runs")
```
#Hair color is an atrribute with different levels for each of the hair colors.
#All of these are called factors in this termonology. Color of our eyes, or hair are these factors
standing<-c("junior","freshmen","junior","Sophmore","Senior")
# class(standing) Allows you to check what variable is made up of... in this case characters
#Store the standing back into itself as this new factor version
standing<-factor(standing,levels=c("freshmen","sophmores","junior","senior"))
#You must order the table how YOU want it to be done^
```{r}
query<-"SELECT weight 
FROM Master"
#Good example of storing all the data into a variable that you
#Can use elsewhere in your code
result<-sqldf(query)
#Issue with all clors default making it this bright pink
ggplot()+
  geom_histogram(data=result,aes(x=weight),color="blue",fill="white",bins=50)+
  ggtitle("Body-Weight of the fat baseball players")

```

